---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
load("brfss2013.RData")
```



* * *

## Part 1: Data
The data were collected by telephone-based survey, divided into two main categories, landline telephone-based survey and cellular telephone-based survey. In the former method, the random adult from the household is selected. In the latter method, the survey is proceeded by selecting the participater who is living in the private residence or college housing using cellular telephone

There were no experiment conducted, the data from the survey is an observation, so the result from the survey only imply correlation, not causation

The survey data are collected across the US, so it could be generalized to the population of the US.

* * *

## Part 2: Research questions

**Research quesion 1:**

**Research quesion 2:**

**Research quesion 3:**


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}

```



**Research quesion 2:**

```{r}

```



**Research quesion 3:**

```{r}

```

