---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
load("brfss2013.RData")
```



* * *

## Part 1: Data
The data were collected by telephone-based survey, divided into two main categories, landline telephone-based survey and cellular telephone-based survey. In the former method, the random adult from the household is selected. In the latter method, the survey is proceeded by selecting the participater who is living in the private residence or college housing using cellular telephone

There were no experiment conducted, the data from the survey is an observation, so the result from the survey only imply correlation, not causation

The survey data are collected across the US, the sample is large enough to be generalized to the population of the US.

* * *

## Part 2: Research questions

**Research quesion 1:**
Is there any correlation between the number of children and the satisfaction of life? Furthermore, are there any noticable difference in this correlation among the difference level of income?

### Discussion
This question is interesting because there were several discussion on the internet forum talking positively and negatively about their kids , which may not be the good representative to the whole population because people who are more upfront may be the group of people who have an strong opinions about something.

### Used variable:
- lsatisfy: Satisfaction With Life
- children: Number Of Children In Household
- income2: Income Level

**Research quesion 2:**
Is there any correlation between the number of children and the level of income?

### Discussion
This question use the same variable as the question 1, but shift the focus to different topic. Eventhough people with higher income should be able to afford more children compared to the people with lower income, but generally I have seen alot of people with lower income with a lot of children. So it was quite interesting question to me to see the actual result from the collected survey

### Used variable:
- children: Number Of Children In Household
- income2: Income Level

**Research quesion 3:**
Are there any relationship between the smoking status, alcohol consuming status and poor physical health status

### Discussion
Smoking and consuming alcohol are tend to be done together. So  it would be interesting to see if they will affect the person's health or not

### Used variable:
- _smoker3: Computed Smoking Status
- _rfdrhv4: Heavy Alcohol Consumption Calculated Variable

* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}

```



**Research quesion 2:**

```{r}
df <- data.frame(brfss2013$smokday2,brfss2013$chcocncr)
df <- df[complete.cases(df),]
ggplot(df,aes(brfss2013.smokday2,..count..)) + 
  geom_bar(aes(fill = brfss2013.chcocncr),position = "fill") +
  labs(x = "Frequency of smoking", fill = 'Told having cancer')
```



**Research quesion 3:**

```{r}

```

